Constraining tensorial and scalar couplings with $B\to K\bar\mu\mu$ and $B_s\to \bar\mu\mu$

### 2015-04-29 tensor/draft/draft-tensor-op.tex
[draft-tensor-op.tex] removed comments on R_K measurement, updated first row in scTT5_FH, appendix: no FF-relations in tensor amplitudes of B->K* ll

The SM values $\wilson[\ell]{7,9,10}$ are obtained at next-to-next-to leading order
(NNLO) \cite{Bobeth:2003at, Huber:2005ig} and depend on the fundamental parameters
of the top-quark and $W$-boson masses, as well as on the sine of the weak mixing angle.
Moreover, they are universal for the three lepton flavors $\ell = e,\, \mu,\, \tau$.
All other Wilson coefficients are numerically suppressed or zero:
$\wilson[SM]{7'} = m_s/m_b\, \wilson[SM]{7}$, $\wilson[SM]{S,S',P,P'} \sim
{\cal O}(m_b^2/m_W^2)$, and $\wilson[SM]{9',10',T,T5} = 0$. Beyond the SM,
lepton-flavor non-universal effects are possible in principle and have been
discussed for example recently \cite{Alonso:2014csa, Hiller:2014yaa, Ghosh:2014awa,
Biswas:2014gga, Hurth:2014vma, Glashow:2014iga, Altmannshofer:2014rta, Hiller:2014abc} in
connection with the measurement of $R_K = {\cal B}_\mu/{\cal B}_e$ in
$q^2 \in [1, 6]$ GeV$^2$ \cite{Aaij:2014ora}, which deviates by $2.6\sigma$
from the SM prediction $R_K^{\rm SM} = 1.00$ \cite{Bobeth:2007dw, Bouchard:2013mia}.

@@

\begin{figure*}
  \setlength{\relwidth}{0.31\textwidth}
  \includegraphics[width=\relwidth]{plots/pdf/ct_K_FH1to6}
  \includegraphics[width=\relwidth]{plots/pdf/ct_K_FH15to22}
  \\
  \includegraphics[width=\relwidth]{plots/pdf/ct_K_BR1to6}
  \includegraphics[width=\relwidth]{plots/pdf/ct_K_BR15to22}
  \\
  \includegraphics[width=.24\textwidth]{plots/pdf/Br-Kstar-1-6_vs_cT.pdf}
  \includegraphics[width=.24\textwidth]{plots/pdf/Br-Kstar-14-16_vs_cT.pdf}
  \includegraphics[width=.24\textwidth]{plots/pdf/Br-Kstar-16-19_vs_cT.pdf}
  \caption{
    \eos{The sensitivity of $F_H^\mu$ [upper row: 1, 2], ${\cal B}(B^+ \to K^+
    \bar\mu\mu)$ [upper row: 3, 4] and ${\cal B}(B^0 \to K^{*0} \bar\mu\mu)$
    [lower row] integrated over $q^2$ at low and high $q^2$ to the tensorial
    coupling $\wilson{T}$. The bands represent the theory uncertainties at
    68\% probability.
    For comparison two values of $\wilson[NP]{9} = 0$ (red) and $\wilson[NP]{9}
    = -1.3$ (green) are shown together with the 68\% measurements of LHCb (blue).}
  }
  \label{fig:FHvsCT}
\end{figure*}

@@

\begin{table*}
  \renewcommand{\arraystretch}{1.3}
  %\resizebox{\textwidth}{!}{
  \begin{tabular}{c|ccc}
  \hline
  data set
  & only $F_H^\mu$
  & $F_H^\mu$ + other
  & $F_H^\mu$ + other
  \\
  set of couplings
  & $\wilson{T,\,T5}$
  & $\wilson{T,\,T5}$
  & $\wilson{T,\,T5,\, 9,\,10}$
  \\
  \hline \hline
  $\mbox{Re}\,\wilson{T}$
  & $\quad$ $[-0.31,\, 0.16]$ ($[-0.51,\, 0.34]$) $\quad$
  & \eos{$\quad$ $[-0.19,\, 0.13]$ ($[-0.34,\, 0.27]$) $\quad$}
  & \eos{$\quad$ $[-0.20,\, 0.20]$ ($[-0.40,\, 0.35]$) $\quad$}
  \\
  $\mbox{Im}\,\wilson{T}$
  & $[-0.23,\, 0.24]$ ($[-0.43,\, 0.43]$)
  & \eos{$[-0.16,\, 0.17]$ ($[-0.31,\, 0.31]$)}
  & \eos{$[-0.20,\, 0.20]$ ($[-0.35,\, 0.35]$)}
  \\[0.1cm]
  $\mbox{Re}\,\wilson{T5}$
  & $[-0.24,\, 0.25]$ ($[-0.43,\, 0.44]$)
  & \eos{$[-0.07,\, 0.25]$ ($[-0.23,\, 0.38]$)}
  & \eos{$[-0.20,\, 0.15]$ ($[-0.35,\, 0.35]$)}
  \\
  $\mbox{Im}\,\wilson{T5}$
  & $[-0.25,\, 0.24]$ ($[-0.44,\, 0.44]$)
  & \eos{$[-0.17,\, 0.16]$ ($[-0.31,\, 0.31]$)}
  & \eos{$[-0.20,\, 0.20]$ ($[-0.35,\, 0.35]$)}
  \\
  \hline
  $|\wilson{T}|$, $|\wilson{T5}|$
  & $[0.13,\, 0.42]$ ($[0.04,\, 0.56]$)
  & \eos{$< 0.25$ ($< 0.35$)}
  & \eos{$< 0.30$ ($< 0.45$)}
  \\
  \hline
  \end{tabular}
%}
  \renewcommand{\arraystretch}{1.0}
  \caption{
     \label{tab:cTT5:1-dimCLs}
     The constraints on complex-valued $\wilson{T,\,T5}$ --- [upper] 1D-marginalized
     at 68\% (95\%) probability and [lower] 2D-marginalized --- when using
     measurements of $i)$ only $F_H^\mu$, $ii)$ $F_H^\mu$ and other data in
     \reftab{tab:observables} (except $\overline{\cal B}(B_s \to \bar\mu\mu)$), and $iii)$ allowing
     also new physics contributions to $\wilson{9,\,10}$ with uniform prior
     $\mbox{Re},\mbox{Im}(\wilson[NP]{i}) \in [-7,\, 7]$.
  }
\end{table*}

@@

\begin{table*}
  \renewcommand{\arraystretch}{1.3}
  %\resizebox{\textwidth}{!}{
  \begin{tabular}{c|ccc}
  \hline
  data set
  & only $F_H^\mu$
  & only $\overline{\cal B}(B_s \to \bar\mu\mu)$
  & all
  \\
  set of couplings
  & $\wilson{S,\,S',\,P,\,P'}$
  & $\wilson{S,\,S',\,P,\,P'}$
  & $\wilson{S,\,S',\,P,\,P'\,10,\,10'}$
  \\
  \hline \hline
  $\mbox{Re}(\wilson{S} - \wilson{S'})$
  & $\quad$ $-$ $\quad$
  & \eos{$\quad$ $[-0.08,\, 0.08]$ ($[-0.12,\, 0.12]$) $\quad$}
  & \eos{$\quad$ $[-0.08,\, 0.08]$ ($[-0.12,\, 0.12]$) $\quad$}
  \\
  $\mbox{Im}(\wilson{S} - \wilson{S'})$
  & $\quad$ $-$ $\quad$
  & \eos{$\quad$ $[-0.08,\, 0.08]$ ($[-0.12,\, 0.12]$) $\quad$}
  & \eos{$\quad$ $[-0.08,\, 0.08]$ ($[-0.12,\, 0.12]$) $\quad$}
  \\[0.1cm]
  $\mbox{Re}(\wilson{S} + \wilson{S'})$
  & \eos{$[-0.4,\, 0.4]$ ($[-0.7,\, 0.7]$)}
  & $-$
  & \eos{$[-0.3,\, 0.4]$ ($[-0.6,\, 0.7]$)}
  \\
  $\mbox{Im}(\wilson{S} + \wilson{S'})$
  & \eos{$[-0.4,\, 0.4]$ ($[-0.7,\, 0.7]$)}
  & $-$
  & \eos{$[-0.4,\, 0.4]$ ($[-0.7,\, 0.7]$)}
  \\[0.1cm]
  $\mbox{Re}(\wilson{P} - \wilson{P'})$
  & $-$
  & \eos{$[0.06,\, 0.20]$  ($[0.02,\, 0.25]$)}
  & \eos{$[-0.10,\, 0.10]$ ($[-0.18,\, 0.18]$)}
  \\
  $\mbox{Im}(\wilson{P} - \wilson{P'})$
  & $-$
  & \eos{$[-0.08,\, 0.08]$ ($[-0.12,\, 0.12]$)}
  & \eos{$[-0.10,\, 0.10]$ ($[-0.20,\, 0.20]$)}
  \\[0.1cm]
  $\mbox{Re}(\wilson{P} + \wilson{P'})$
  & \eos{$[-0.2,\, 0.6]$ ($[-0.5,\, 0.9]$)}
  & $-$
  & \eos{$[-0.4,\, 0.4]$ ($[-0.7,\, 0.7]$)}
  \\
  $\mbox{Im}(\wilson{P} + \wilson{P'})$
  & \eos{$[-0.4,\, 0.4]$ ($[-0.7,\, 0.7]$)}
  & $-$
  & \eos{$[-0.4,\, 0.4]$ ($[-0.7,\, 0.7]$)}
  \\
  \hline
  \end{tabular}
%}
  \renewcommand{\arraystretch}{1.0}
  \caption{
     \label{tab:cSP:1-dimCLs}
     The constraints on complex-valued $\wilson{S,\,S',\,P,\,P'}$ --- 1D-marginalized
     at 65\% (95\%) probability --- when using measurements of $i)$ only $F_H^\mu$,
     $ii)$ only $\overline{\cal B}(B_s \to \bar\mu\mu)$ and $iii)$ all the data in
     \reftab{tab:observables} allowing also for new physics contributions to
     $\wilson{10,\,10'}$ with \eos{uniform prior $\mbox{Re}\,\wilson[NP]{10} \in [-1,\, 9]$,
     $\mbox{Im}\,(\wilson[NP]{10})$ and $\mbox{Re},\mbox{Im}\,(\wilson[NP]{10'}) \in [-5,\, 5]$}.
  }
\end{table*}

@@

Finally we discuss the possibility of suitable normalisations of $J_{6c}$,
$(J_{1s} - 3\, J_{2s})$ and $(J_{1c} + J_{2c})$ at high $q^2$ that would provide
optimised observables. For this purpose we use form factor relations at leading
order in $1/m_b$ and neglect terms suppressed by $m_\ell/\sqrt{q^2}$. With the
notation and expressions derived in \cite{Bobeth:2012vn},
\begin{equation}
\begin{aligned}
  J_{1s} - 3\, J_{2s} & = \frac{3}{2}\, \rho_1^T (f_\perp^2 + f_\parallel^2) \,,
\\[0.1cm]
  J_{1c} + J_{2c} & = 3\, \rho_1^T f_0^2
     + \frac{3 N^2 \lambda}{(m_b+m_s)^2} A_0^2
\\
   & \quad \times \left(|\wilson{S}-\wilson{S'}|^2 + |\wilson{P}-\wilson{P'}|^2\right)\,.
\\[0.1cm]
  \frac{4}{3} J_{6c} & = \todo{???}
\end{aligned}
\end{equation}
Here $f_{\perp, \parallel, 0}$ and $A_0$ denote $B\to K^*$ form factors, whereas
the $\rho_1^\pm$ depends on vectorial couplings and $\rho_1^T \propto
(|\wilson{T}|^2 + |\wilson{T5}|^2)$.

@@

The tensorial and scalar amplitudes in $B\to K^{(*)} \bar\ell\ell$ factorize naively,
i.e. they depend only on scalar and tensor $B\to K^{(*)}$ form factors. These amplitudes
are implemented in {\tt EOS} for $B\to K \bar\ell\ell$ and $B\to K^* \bar\ell\ell$ as
given in \cite{Bobeth:2007dw} and \cite{Bobeth:2012vn}, respectively. In the case
of $B\to K\bar\ell\ell$, we refrain from using respective form factor relations at
large and low recoil for the tensor and scalar form factors, $f_T$ and $f_0$ in the
corresponding amplitudes. In the case of $B\to K^*\bar\ell\ell$, we use the scalar
form factor $A_0$ in the scalar and time-like amplitudes, but apply form factor
relations in tensor amplitudes for the tensor form factors $T_{1,2,3}$.

>>>>

The SM values $\wilson[\ell]{7,9,10}$ are obtained at next-to-next-to leading order
(NNLO) \cite{Bobeth:2003at, Huber:2005ig} and depend on the fundamental parameters
of the top-quark and $W$-boson masses, as well as on the sine of the weak mixing angle.
Moreover, they are universal for the three lepton flavors $\ell = e,\, \mu,\, \tau$.
All other Wilson coefficients are numerically suppressed or zero:
$\wilson[SM]{7'} = m_s/m_b\, \wilson[SM]{7}$, $\wilson[SM]{S,S',P,P'} \sim
{\cal O}(m_b^2/m_W^2)$, and $\wilson[SM]{9',10',T,T5} = 0$. 
%Beyond the SM,
%lepton-flavor non-universal effects are possible in principle and have been
%discussed for example recently \cite{Alonso:2014csa, Hiller:2014yaa, Ghosh:2014awa,
%Biswas:2014gga, Hurth:2014vma, Glashow:2014iga, Altmannshofer:2014rta, Hiller:2014abc} in
%connection with the measurement of $R_K = {\cal B}_\mu/{\cal B}_e$ in
%$q^2 \in [1, 6]$ GeV$^2$ \cite{Aaij:2014ora}, which deviates by $2.6\sigma$
%from the SM prediction $R_K^{\rm SM} = 1.00$ \cite{Bobeth:2007dw, Bouchard:2013mia}.

@@

\begin{figure*}
  \setlength{\relwidth}{0.31\textwidth}
  \includegraphics[width=\relwidth]{plots/pdf/ct_K_FH1to6}
  \includegraphics[width=\relwidth]{plots/pdf/ct_K_FH15to22}
  \\
  \includegraphics[width=\relwidth]{plots/pdf/ct_K_BR1to6}
  \includegraphics[width=\relwidth]{plots/pdf/ct_K_BR15to22}
  \\
  \includegraphics[width=.24\textwidth]{plots/pdf/Br-Kstar-1-6_vs_cT.pdf}
  \includegraphics[width=.24\textwidth]{plots/pdf/Br-Kstar-14-16_vs_cT.pdf}
  \includegraphics[width=.24\textwidth]{plots/pdf/Br-Kstar-16-19_vs_cT.pdf}
  \caption{
    \eos{The sensitivity of $F_H^\mu$ [upper row], ${\cal B}(B^+ \to K^+
    \bar\mu\mu)$ [middle row] and ${\cal B}(B^0 \to K^{*0} \bar\mu\mu)$
    [lower row] integrated over low- and high-$q^2$ bins to the tensorial
    coupling $\wilson{T}$. The bands represent the theory uncertainties at
    68\% probability.
    For comparison two values of $\wilson[NP]{9} = 0$ (blue) and $\wilson[NP]{9}
    = -1.1$ (red) are shown together with the 68\% measurements of LHCb (grey).}
  }
  \label{fig:FHvsCT}
\end{figure*}

@@

\begin{table*}
  \renewcommand{\arraystretch}{1.3}
  %\resizebox{\textwidth}{!}{
  \begin{tabular}{c|ccc}
  \hline
  data set
  & only $F_H^\mu$
  & $F_H^\mu$ + other
  & $F_H^\mu$ + other
  \\
  set of couplings
  & $\wilson{T,\,T5}$
  & $\wilson{T,\,T5}$
  & $\wilson{T,\,T5,\, 9,\,10}$
  \\
  \hline \hline
  $\mbox{Re}\,\wilson{T}$
  & $\quad$ $[-0.32,\, 0.16]$ ($[-0.52,\, 0.35]$) $\quad$
  & \eos{$\quad$ $[-0.19,\, 0.13]$ ($[-0.34,\, 0.27]$) $\quad$}
  & \eos{$\quad$ $[-0.20,\, 0.20]$ ($[-0.40,\, 0.35]$) $\quad$}
  \\
  $\mbox{Im}\,\wilson{T}$
  & $[-0.25,\, 0.24]$ ($[-0.44,\, 0.44]$)
  & \eos{$[-0.16,\, 0.17]$ ($[-0.31,\, 0.31]$)}
  & \eos{$[-0.20,\, 0.20]$ ($[-0.35,\, 0.35]$)}
  \\[0.1cm]
  $\mbox{Re}\,\wilson{T5}$
  & $[-0.25,\, 0.24]$ ($[-0.44,\, 0.44]$)
  & \eos{$[-0.07,\, 0.25]$ ($[-0.23,\, 0.38]$)}
  & \eos{$[-0.20,\, 0.15]$ ($[-0.35,\, 0.35]$)}
  \\
  $\mbox{Im}\,\wilson{T5}$
  & $[-0.24,\, 0.25]$ ($[-0.44,\, 0.45]$)
  & \eos{$[-0.17,\, 0.16]$ ($[-0.31,\, 0.31]$)}
  & \eos{$[-0.20,\, 0.20]$ ($[-0.35,\, 0.35]$)}
  \\
  \hline
  $|\wilson{T}|$, $|\wilson{T5}|$
  & $[0.13,\, 0.43]$ ($[0.03,\, 0.57]$)
  & \eos{$< 0.25$ ($< 0.35$)}
  & \eos{$< 0.30$ ($< 0.45$)}
  \\
  \hline
  \end{tabular}
%}
  \renewcommand{\arraystretch}{1.0}
  \caption{
     \label{tab:cTT5:1-dimCLs}
     The constraints on complex-valued $\wilson{T,\,T5}$ --- [upper] 1D-marginalized
     at 68\% (95\%) probability and [lower] 2D-marginalized --- when using
     measurements of $i)$ only $F_H^\mu$, $ii)$ $F_H^\mu$ and other data in
     \reftab{tab:observables} (except $\overline{\cal B}(B_s \to \bar\mu\mu)$), and $iii)$ allowing
     also new physics contributions to $\wilson{9,\,10}$ with uniform prior
     $\mbox{Re},\mbox{Im}(\wilson[NP]{i}) \in [-7,\, 7]$.
  }
\end{table*}

@@

\begin{table*}
  \renewcommand{\arraystretch}{1.3}
  %\resizebox{\textwidth}{!}{
  \begin{tabular}{c|ccc}
  \hline
  data set
  & only $F_H^\mu$
  & only $\overline{\cal B}(B_s \to \bar\mu\mu)$
  & all
  \\
  set of couplings
  & $\wilson{S,\,S',\,P,\,P'}$
  & $\wilson{S,\,S',\,P,\,P'}$
  & $\wilson{S,\,S',\,P,\,P',\,9,\,9',\,10,\,10'}$
  \\
  \hline \hline
  $\mbox{Re}(\wilson{S} - \wilson{S'})$
  & $\quad$ $-$ $\quad$
  & \eos{$\quad$ $[-0.08,\, 0.08]$ ($[-0.12,\, 0.12]$) $\quad$}
  & \eos{$\quad$ $[-0.08,\, 0.08]$ ($[-0.12,\, 0.12]$) $\quad$}
  \\
  $\mbox{Im}(\wilson{S} - \wilson{S'})$
  & $\quad$ $-$ $\quad$
  & \eos{$\quad$ $[-0.08,\, 0.08]$ ($[-0.12,\, 0.12]$) $\quad$}
  & \eos{$\quad$ $[-0.08,\, 0.08]$ ($[-0.12,\, 0.12]$) $\quad$}
  \\[0.1cm]
  $\mbox{Re}(\wilson{S} + \wilson{S'})$
  & \eos{$[-0.4,\, 0.4]$ ($[-0.7,\, 0.7]$)}
  & $-$
  & \eos{$[-0.3,\, 0.4]$ ($[-0.6,\, 0.7]$)}
  \\
  $\mbox{Im}(\wilson{S} + \wilson{S'})$
  & \eos{$[-0.4,\, 0.4]$ ($[-0.7,\, 0.7]$)}
  & $-$
  & \eos{$[-0.4,\, 0.4]$ ($[-0.7,\, 0.7]$)}
  \\[0.1cm]
  $\mbox{Re}(\wilson{P} - \wilson{P'})$
  & $-$
  & \eos{$[0.06,\, 0.20]$  ($[0.02,\, 0.25]$)}
  & \eos{$[-0.10,\, 0.10]$ ($[-0.18,\, 0.18]$)}
  \\
  $\mbox{Im}(\wilson{P} - \wilson{P'})$
  & $-$
  & \eos{$[-0.08,\, 0.08]$ ($[-0.12,\, 0.12]$)}
  & \eos{$[-0.10,\, 0.10]$ ($[-0.20,\, 0.20]$)}
  \\[0.1cm]
  $\mbox{Re}(\wilson{P} + \wilson{P'})$
  & \eos{$[-0.2,\, 0.6]$ ($[-0.5,\, 0.9]$)}
  & $-$
  & \eos{$[-0.4,\, 0.4]$ ($[-0.7,\, 0.7]$)}
  \\
  $\mbox{Im}(\wilson{P} + \wilson{P'})$
  & \eos{$[-0.4,\, 0.4]$ ($[-0.7,\, 0.7]$)}
  & $-$
  & \eos{$[-0.4,\, 0.4]$ ($[-0.7,\, 0.7]$)}
  \\
  \hline
  \end{tabular}
%}
  \renewcommand{\arraystretch}{1.0}
  \caption{
     \label{tab:cSP:1-dimCLs}
     The constraints on complex-valued $\wilson{S,\,S',\,P,\,P'}$ --- 1D-marginalized
     at 65\% (95\%) probability --- when using measurements of $i)$ only $F_H^\mu$,
     $ii)$ only $\overline{\cal B}(B_s \to \bar\mu\mu)$ and $iii)$ all the data in
     \reftab{tab:observables} allowing also for new physics contributions to
     $\wilson{10,\,10'}$ with \eos{uniform prior $\mbox{Re}\,\wilson[NP]{10} \in [-1,\, 9]$,
     $\mbox{Im}\,(\wilson[NP]{10})$ and $\mbox{Re},\mbox{Im}\,(\wilson[NP]{10'}) \in [-5,\, 5]$}.
  }
\end{table*}

@@

Finally we discuss the possibility of suitable normalisations of $J_{6c}$,
$(J_{1s} - 3\, J_{2s})$ and $(J_{1c} + J_{2c})$ at high $q^2$ that would provide
optimised observables. For this purpose we use form factor relations at leading
order in $1/m_b$ and neglect terms suppressed by $m_\ell/\sqrt{q^2}$. With the
notation and expressions derived in \cite{Bobeth:2012vn},
\begin{equation}
\begin{aligned}
  J_{1s} - 3\, J_{2s} & = \frac{3}{2}\, \rho_1^T (f_\perp^2 + f_\parallel^2) \,,
\\[0.1cm]
  J_{1c} + J_{2c} & = 3\, \rho_1^T f_0^2
     + \frac{3 N^2 \lambda}{(m_b+m_s)^2} A_0^2
\\
   & \quad \times \left(|\wilson{S}-\wilson{S'}|^2 + |\wilson{P}-\wilson{P'}|^2\right)\,.
%\\[0.1cm]
%  \frac{4}{3} J_{6c} & = \todo{???}
\end{aligned}
\end{equation}
Here $f_{\perp, \parallel, 0}$ and $A_0$ denote $B\to K^*$ form factors, whereas
the $\rho_1^\pm$ depends on vectorial couplings and $\rho_1^T \propto
(|\wilson{T}|^2 + |\wilson{T5}|^2)$.

@@

The tensorial and scalar amplitudes in $B\to K^{(*)} \bar\ell\ell$ factorize naively,
i.e. they depend only on scalar and tensor $B\to K^{(*)}$ form factors. These amplitudes
are implemented in {\tt EOS} for $B\to K \bar\ell\ell$ and $B\to K^* \bar\ell\ell$ as
given in \cite{Bobeth:2007dw} and \cite{Bobeth:2012vn}, respectively and we refrain from
using respective form factor relations at large and low recoil for the tensor and scalar
$B\to K$ and $B\to K^*$ form factors.
